Flesh Simulation in the Field of Animation

### 2020-04-09 LaTeX-Master-Vorlage/chapter/paper.tex
changes

\textbf{3. Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object which influences the deformation. But when we remove all the forces, the object should be back in its rest state.

@@

\subsubsection{1D Length Term}
Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
\]
that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F}, we get the following term:
\[
\Psi_{M}=\frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]
This energy reaches its minimum at a zero volume state, meaning $I_{C}=0$. Mooney added the hard constraint that $J$ should be equal to $1$, so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin. Note that the energy is singularity free and well defined under inversion.

@@

\subsubsection{3D Volume Term}
The volume term of $\Psi_{Neo}$, meaning
\[
\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
\]
results in numerical problems, since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion, $\Psi_{Neo, volume}$ is not singularity free. 
The same applies for the 3D volume term of $\Psi_{A}$, namely
\[
\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
\]
The term of $\Psi_{A}$ and $\Psi_{B}$ which is of the form
\[
\Psi_{M} = \frac{\lambda}{2}(J-1)^{2}
\]
does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$, which is defined as
\[
\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}.
\]
$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable which will be discussed in the next section.

@@

If the energy had rest stability, $P_{D}(\mathbf{I})$ would resolve to zero. Unfortunately, this is not the case here. In order to solve this problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$. Using this modification, the energy can written as
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
\]

@@

\subsection{Meta-Stability under Degeneracy}
We have seen that he energy $\Psi_{E}$ has inversion, reflection and rest stability. Now we are interested how it behaves under degeneracy. The authors of the paper \textit{\acrshort{snh}} viewed this as a Drucker stability analysis (see \cite{bower2009applied}). By Drucker stability, we mean a set of criteria that a material can satisfy or not. This is a measurement of the stability of the material. The calculations can be found in the supplemental material of \textit{\acrshort{snh}}, I will only present the results here.

The energy remains stable when crushing the object into a \textit{plane}. The object is able to return to its rest state. Thus, no further adjustments needs to be done. When crushing the object into a \textit{line}, the energy is meta-stable. A meta-stable state is a weaker state of stability that is resistant to small changes but not to large ones. The alternative would be a state that yields singularities, which worsens the situation. Hence, we can leave the energy as it is. Crushing the object to a \textit{point}, the material cannot recover into its rest state. This effect is small for a higher poisson's ratio as for biological tissue. For completeness the authors nevertheless added a regularized origin barrier:
\[
	\Psi_{origin} = \operatorname{log}(I_C +\delta)
\]
This term eliminates the point meta-stability for a positive poisson's ratio without interfering with the other requirements for the energy. It can be shown that the value $\delta$ should be set to $1$. This is also included in the supplemental material of the paper (\cite{Smith:2018:SNF:3191713.3180491}, 12:4).

@@

\subsection{First Piola-Kirchhoff Stress (PK1)}
In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$:
\begin{align*}
P(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \frac{\partial}{\partial \mathbf{F}} \left[\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F})+1\right)\right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1} \\
&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}}
\end{align*}

@@

\subsubsection{Mu}
The Mu term has the same structure with different entries. It can be obtained by $\mathbf{F} f_i$ and has the form
\[
\mathbb{M} = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
\]
When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal:
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}
\]
This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$:
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal
\]
This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues, we can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm introduced in Def. \ref{FN} and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the \acrshort{svd} of $\mathbf{F}$ stated in Eq. \ref{eq:svd_simga}. The equation can be obtained by using Eq. \ref{eq:FN}, explained in chapter 2. The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.

@@

\todoredefined[inline]{
TODO: Check again each $f_1$ and $-$ in vectorization of H.
}

@@

\subsection{The Complete Eigensystem}

\todoredefined[inline]{
TODO: Include what is necessary.
}

>>>>

\textbf{3. Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object, which influences the deformation. But when we remove all the forces, the object should be back in its rest state.

@@

\subsubsection{1D Length Term}
Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right),
\]
which is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F}, we get the following term:
\[
\Psi_{M}=\frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]
This energy reaches its minimum at a zero volume state, meaning $I_{C}=0$. Mooney added the hard constraint that $J$ should be equal to $1$, so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin. Note that the energy is singularity free and well defined under inversion.

@@

\subsubsection{3D Volume Term}
The volume term of $\Psi_{Neo}$, meaning
\[
\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2},
\]
results in numerical problems, since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion, $\Psi_{Neo, volume}$ is not singularity free. 
The same applies for the 3D volume term of $\Psi_{A}$, namely
\[
\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
\]
The term of $\Psi_{A}$ and $\Psi_{B}$, which is of the form
\[
\Psi_{M} = \frac{\lambda}{2}(J-1)^{2},
\]
does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$, which is defined as
\[
\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}.
\]
$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable, which will be discussed in the next section.

@@

If the energy had rest stability, $P_{D}(\mathbf{I})$ would resolve to zero. Unfortunately, this is not the case here. In order to solve this problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$. Using this modification, the energy can be written as
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
\]

@@

\subsection{Meta-Stability under Degeneracy}
We have seen that he energy $\Psi_{E}$ has inversion, reflection and rest stability. Now we are interested in how it behaves under degeneracy. The authors of the paper \textit{\acrshort{snh}} viewed this as a Drucker stability analysis (see \cite{bower2009applied}). By Drucker stability, we mean a set of criteria that a material can satisfy or not. This is a measurement of the stability of the material. The calculations can be found in the supplemental material of \textit{\acrshort{snh}}, I will only present the results here.

The energy remains stable when crushing the object into a \textit{plane}. The object is able to return to its rest state. Thus, no further adjustments need to be done. When crushing the object into a \textit{line}, the energy is meta-stable. A meta-stable state is a weaker state of stability that is resistant to small changes but not to large ones. The alternative would be a state that yields singularities, which worsens the situation. Hence, we can leave the energy as it is. After crushing the object to a \textit{point}, the material cannot recover into its rest state. This effect is small for a higher poisson's ratio. For completeness the authors nevertheless added a regularized origin barrier:
\[
	\Psi_{origin} = \operatorname{log}(I_C +\delta)
\]
This term eliminates the point meta-stability for a positive poisson's ratio, without interfering with the other requirements for the energy. It can be shown that the value $\delta$ should be set to $1$. This is also included in the supplemental material of the paper (\cite{Smith:2018:SNF:3191713.3180491}, 12:4).

@@

\subsection{First Piola-Kirchhoff Stress (PK1)}
In order to analyse the energy, PK1 can be used for Eq. \ref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$:
\begin{align*}
P(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \frac{\partial}{\partial \mathbf{F}} \left[\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F})+1\right)\right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1} \\
&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}}
\end{align*}

@@

\subsubsection{Mu}
The Mu term has the same structure with different entries. It can be obtained by $\mathbf{F} f_i$ and has the form
\[
\mathbb{M} = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
\]
When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal:
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}
\]
This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$:
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal
\]
This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues, we can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right),
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm introduced in Def. \ref{FN} and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the \acrshort{svd} of $\mathbf{F}$ stated in Eq. \ref{eq:svd_simga}. The equation can be obtained by using Eq. \ref{eq:FN}, explained in chapter 2. The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.

@@

@@

\subsection{The Complete Eigensystem}
With these expressions for each individual term, we can now analyse the complete system, which will be called $\mathbf{\check{A}}$.
\[
	\mathbf{\check{A}} = \mu \left(1-\frac{1}{I_C+1} \right) \mathbf{I} + \mu \frac{2}{(I_C +1)^2} \mathbf{\check{f}\check{f}}^\intercal + \lambda \mathbf{\check{g}\check{g}}^\intercal + \lambda (J-\alpha) \mathbf{\check{H}}
\]
Deriving the eigenvalues from $\mathbf{\check{A}}$ is nontrivial. Therefore, I will not include the calculations here and will only present the results. An interested reader can have a look at the paper \textit{\acrshort{snh}} on p.12:7 and 12:8.

The final eigenvalues are
\begin{align*}
	&\epsilon_k = \lambda (J-\alpha) \bar{\epsilon}_k + \mu_T		&k = 0, 1, 2
\end{align*}	
and 
\begin{align*}
	&\epsilon_3 = \lambda(J-\alpha)\sigma_0 + \mu_T	&\epsilon_6 = -\lambda (J-\alpha)\sigma_0 + \mu_T \\
	&\epsilon_4 = \lambda(J-\alpha)\sigma_1 + \mu_T	&\epsilon_7 = -\lambda (J-\alpha)\sigma_1 + \mu_T \\
	&\epsilon_5 = \lambda(J-\alpha)\sigma_2 + \mu_T	&\epsilon_8 = -\lambda (J-\alpha)\sigma_2 + \mu_T.
\end{align*}

The variable $\mu_T$ is equal to $\mu(1- \frac{1}{I_C +1})$ and serves as a regularization term. $\bar{\epsilon}_k$ are the roots of the equation
\[
	\bar{\epsilon}^3 + c_2 \bar{\epsilon}^2 + c_1 \bar{\epsilon} + c_0 = 0.
\]
The variables $c_0$, $c_1$ and $c_2$ are defined as
\begin{align*}
	c_2 &= - \|\mathbf{\check{g}}\|^2_2 \rho - I_C \eta \\
	c_1 &= - (1+ 2J\rho)I_C - 6 J \eta + \left( \|\mathbf{\check{g}}\|^2_2 I_C - 9J^2 \right) \rho \eta	\\
	c_0 &= - (2 +3J\rho)J + \left( I_C^2 - 4 \|\mathbf{\check{g}}\|^2_2 \right) \eta + 2J \left( I^2_C -3 \|\mathbf{\check{g}}\|^2_2 \right) \rho \eta 	\\
\end{align*}
with 
\begin{align*}
	&\eta = \frac{2\mu}{(I_C+1)^2 \left( \lambda (J-1) - \frac{3}{4}\mu \right)}		&\rho = \frac{\lambda}{\lambda (J-1) - \frac{3}{4} \mu}.
\end{align*}

\todoredefined[inline]{
TODO: Not happy with this section.
}
